Parsing Postfix log files

### 2007-11-11 doc/logparser-acronyms.tex
More acronyms. Wrapped all Postfix programs except sendmail in \daemon{}. Added glossary entries for all Postfix programs, some need to be fleshed out. Some corrections. More references.

\newacronym{MTA}{Mail Transfer Agent}{description={
    A Mail Transfer Agent sends and/or receives mail via SMTP\@.
}}

\newacronym{RFC}{Request For Comments}{description={
    The Request For Comments series is a series of proposals defining
    various protocols and file formats, e.g. SMTP\@.  The name is somewhat
    misleading: initially the authors were asking for peer review, but
    these documents are now the de facto standards the Internet runs on.
}}

@@

\newacronym{DFA}{Deterministic Finite Automata}{description={
    XXX EXPLAIN DFA\@.  SHOULD IT BE NFA\@?
}}

@@

>>>>

\newacronym{MTA}{Mail Transfer Agent}{description={
    A Mail Transfer Agent sends and/or receives mail via SMTP.
}}

\newacronym{RFC}{Request For Comments}{description={
    The Request For Comments series is a series of proposals defining
    various protocols and file formats, e.g. SMTP.  The name is somewhat
    misleading: initially the authors were asking for peer review, but
    these documents are now the de facto standards the Internet runs on.
}}

@@

\newacronym{DFA}{Deterministic Finite Automata}{description={
    XXX EXPLAIN DFA.  SHOULD IT BE NFA?
}}

@@

\newacronym{pid}{Process IDentifier}{description={
    There may be multiple copies of any program executing at any one time,
    so the program's name is not suitable as a distinguishing identifier;
    instead each process executing is given a pid which is guaranteed to be
    unique for the lifetime of the process.  Once the process has
    completed, the pid may be reused, as they are drawn from a finite pool.
}}

\newacronym{UCE}{Unsolicited Commercial Email}{description={
    UCE is a more restrictive definition of spam than most people would
    use: it only covers mail that is explicitly commercial, thus excluding
    viruses, Bayesian poisoning mails, backscatter, and those annoying
    chain letters you get from friends.
}}

\newacronym{regex}{Regular Expression}{description={
    Regular expressions are a method of matching patterns in text that are
    explained in detail in~\cite{wikipedia-regex, perlre} .
}}

\newacronym{regexs}{Regular Expressions}{description={
    Regular expressions are a method of matching patterns in text that are
    explained in detail in~\cite{wikipedia-regex, perlre} .
}}
